New_Data_Coherence

### 2019-09-18 Analysis/Coherence_Calculations_New.Rmd
coherence tables

>>>>

#Getting non-zero counts for diseases
count_frame = full_join(dis_slopes_biogrid_count %>% ungroup() %>% dplyr::select(Disease, Count), dis_slopes_string_count %>% ungroup() %>% dplyr::select(Disease, Count), "Disease")

count_frame = full_join(count_frame, dis_slopes_string_filt_count %>% ungroup() %>% dplyr::select(Disease, Count), "Disease") %>% arrange(Disease)
```

```{r}
#Adding counts to full frame and reordering

coherence_disease = coherence_disease %>% arrange(Disease) %>% mutate(`Size of Biogrid Network` = count_frame$Count.x, `Size of String Network` = count_frame$Count.y,`Size of String Filt Network`=count_frame$Count) %>% dplyr::select(Disease:`Number of genes`, `Size of Biogrid Network`:`Size of String Filt Network`, `Biogrid Coherence`:`String Filt P-value`)
